Estimate RSV onset and peak timing

### 2023-01-05 RSV_timing_explain/RSV_timing_tutorial.Rmd
add Dan and Ginny's class materials
update timing materials

>>>>

## Harmonic regression to estimate the peak timing of RSV epidemics

**Note: Most of the following materials came from Dan and Ginny's Lecture notes abd Harmonic Regression by NCSS^[https://www.ncss.com/wp-content/themes/ncss/pdf/Procedures/NCSS/Harmonic_Regression.pdf].**

Please check out:

-  Dan's class: Public Health Surveillance 
\
-  Ginny's class: Quantitative Methods in Infectious Diseases

$$X_t=\mu+R\cos(ft+d)+e_t$$
Where 
\
$X_t$ is the time-series contains a periodic (cyclic) component.
\
$\mu$ is mean of the series.
\
$R$ is the amplitude of seasonality.
\
$f=\frac{1}{period}$ is the frequency of the periodic.
\
$d$ is the phase or horizontal offset.
\
$e_t$ is the random error (noise) of the series.
\
$t$ is the time step

## Pseudo-RSV data: Simulate time series with a 12 month period
Imagine this is RSV case data from 2 states, and we want to investigate the
epidemic characteristics in these states and the lag between states.

```{r simulate, echo=T}
set.seed(123)
  n=120 # 10 years
  t <- seq(1,n)
 amp1=2.5 # high amplitude
 freq=1/12 # frequency = 1/period
 amp2=0.5 # low amplitude

 xt1a=amp1*cos(2*3.14159*t*freq)

#other series shifted by 3 months
 xt2a=amp1*cos(2*3.14159*t*freq+1)

#Simulate some poisson count data
 xt1=rpois(n,exp((1+xt1a)))
 xt2= rpois(n,exp(2+xt2a))
```

## The observed pseudo-RSV cases over time in two states

```{r, echo=T}
 plot(t, xt1,type="l", lwd=3, xaxt="n",bty="l",
      ylab="Cases of RSV", xlab="Month(n)", 
      ylim=range(c(xt1,xt2)))
 lines(t,xt2,col="red")
```
